manual-geostat-TMB

### 2019-01-23 analysis/manual-geostat-TMB.Rmd
Increase knots
knots=100

#### Spatial model
```{r}
spde <- sdmTMB::make_spde(dat$X, dat$Y, n_knots = 50)

@@

#### Plot spatiotemporal random effects
```{r}
plot_map(predictions, "est_re_st") +
  ggtitle("Spatiotemporal random effects only") +
  scale_fill_gradient2()

```

>>>>

#### Spatial model
```{r}
spde <- sdmTMB::make_spde(dat$X, dat$Y, n_knots = 100)

@@

#### Plot spatiotemporal random effects
```{r}
plot_map(predictions, "est_re_st") +
  ggtitle("Spatiotemporal random effects only") +
  scale_fill_gradient2()
```
